Methods to prioritise pop-up active transport infrastructure

### 2020-05-09 article.Rmd
Show full road network in Leeds

```{r hospitals, fig.cap="Overview map of input data, showing the main highway types and location of hospitals in Leeds"}
m1 = tm_shape(r_main[1:1000, ] %>% mutate(`Highway type` = highway2)) +
  tm_lines(col = "Highway type", palette = c("green", "black", "blue", "grey")) +
  tm_shape(h_leeds) + tm_dots(size = 0.5, col = "ParentName", palette = "Dark2", title = "Hospital group") +
  tm_layout(legend.outside = TRUE)
# + tm_text("OrganisationName")
m1
```

>>>>

```{r hospitals, fig.cap="Overview map of input data, showing the main highway types and location of hospitals in Leeds"}
m1 = tm_shape(r_main %>% mutate(`Highway type` = highway2)) +
  tm_lines(col = "Highway type", palette = c("green", "black", "blue", "grey")) +
  tm_shape(h_leeds) + tm_dots(size = 0.5, col = "ParentName", palette = "Dark2", title = "Hospital group") +
  tm_layout(legend.outside = TRUE)
# + tm_text("OrganisationName")
m1
```
